### 2022-08-01 paper/akweury/document.tex
update eval

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_groundtruth.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_normal_f1.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_normal_f2.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_42_-28_normal.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_normal_f4.png}
	\end{subfigure}

		\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_img.png}
		\caption{GT}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_error_f1.png}
		\caption{F1}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_error_f2.png}
		\caption{F2}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_32_12_error.png}
		\caption{F3}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_error_f4.png}
		\caption{F4}
	\end{subfigure}

@@

>>>>

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_groundtruth.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_normal_f1.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_normal_f2.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_normal_f3.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_normal_f4.png}
	\end{subfigure}

		\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_img.png}
		\caption{GT}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_error_f1.png}
		\caption{F1}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_error_f2.png}
		\caption{F2}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_error_f3.png}
		\caption{F3}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/fancy_eval_7_error_f4.png}
		\caption{F4}
	\end{subfigure}

@@

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_14_groundtruth.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_14_normal_SVD.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_14_normal_GCNN-512-269.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_14_normal_Trip-Net-512.png}
	\end{subfigure}

	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_14_img.png}
		\caption{GT}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_14_error_SVD.png}
		\caption{SVD}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_14_error_GCNN-512-269.png}
		\caption{GCNN}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_14_error_Trip-Net-512.png}
		\caption{Trip-Net}
	\end{subfigure}

	\caption{Comparison between different SVD, GCNN and Trip-Net model on $ 512\times 512 $ dataset. The first row is surface normal, the second row is the corresponding errors. }
	\label{fig:high_resolution_eval}
\end{figure}

%% 5 degree metric
\begin{table}[H]
	\centering
	\begin{tabular}{l l l l }
		\tabhead{Metrics} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{Trip-Net} \\
		Mean  					& 20 & 5.43 & \\ 
		\hline
		Median					& 20 & 3.53 & \\ 
		\hline
		$ 5^\circ $ 			& 20 & 0.67 & \\
		\hline
		$ 11.5^\circ $ 			& 20 & 0.89 & \\
		\hline
		$ 22.5^\circ $ 			& 20 & 0.97 & \\
		\hline
		$ 30^\circ $ 			& 20 & 0.98 & \\
	\end{tabular}
	\caption{Evaluation of SVD, GCNN and Trip-Net models on 6 different metrics based on 100 test scenes.}	
	\label{tab:high_resolution_eval}
\end{table}
